\chapter{Skills and Development}
\subsection*{Publications}

\subsubsection*{Peer-Reviewed Publications}
\begin{itemize}
   
\item \textbf{L. S. Hesse\footnote[1]{Indicates equal contribution}}, M. K. Wyburd\footnotemark[1],  M. Aliasi, M. Jenkinson, A. T. Papageorghiou, M. C. Haak and A. I.
L. Namburete “Assessment of Regional Cortical Development Through Fissure Based Gestational
Age Estimation in 3D Fetal Ultrasound.” \textit{Uncertainty for Safe Utilization of Machine Learning in
Medical Imaging, and Perinatal Imaging, Placental and Preterm Image Analysis.} Springer, Cham,
2021. 242-252.

\item \textbf{L. S. Hesse} and A. I. L. Namburete "Improving U-Net Segmentation with Active Contour Based Label Correction." \textit{Annual Conference on Medical Image Understanding and Analysis.} Springer, Cham, 2020.

\item \textbf{L. S. Hesse}, G. Kuling, M. Veta, and A. L. Martel, "Intensity augmentation to improve generalizability of breast segmentation across different MRI scan protocols." \textit{IEEE Transactions on Biomedical Engineering.} 68.3 (2020): 759-770

\end{itemize}

\subsubsection*{Publications in Review}


\begin{itemize}
    \item \textbf{L. S. Hesse} and A. I. L. Namburete. "INSightR-Net: Interpretable Neural Network for Regression using Similarity-based Comparisons to Prototypical Examples" \textit{submitted to MICCAI 2022}
   
    \item \textbf{L. S. Hesse}, M. Aliasi, F. Moser, the INTERGROWTH-21st Consortium, M. C. Haak, W. Xie, M. Jenkinson, and A. I. L. Namberete. "Subcortical Segmentation of the Fetal Brain in 3D Ultrasound using Deep Learning" \textit{in review with NeuroImage - minor corrections.}
    
    
\end{itemize}

\subsubsection*{Conference Presentations}
\begin{itemize} 
    \item \textbf{PIPPI workshop @ MICCAI 2021 - conference proceedings and oral presentation:} "Assessment of Regional Cortical Development through Fissure Based Gestational Age Estimation in 3D Fetal Ultrasound"
    \item \textbf{ISUOG 2021 - oral presentation:} "Automated grading of fetal cortical development using deep learning algorithms: a preliminary three-dimensional ultrasound study in healthy fetuses."
    \item \textbf{OHBM 2021 - poster presentation:} Few-shot subcortical brain structure segmentation in 3D fetal brain ultrasound 
    \item \textbf{MIUA 2020 - conference proceedings and oral presentation:} Improving U-Net Segmentation with Active Contour Based Label Correction
\end{itemize}


\subsection*{Teaching Experience}
\begin{itemize}
    \item \textbf{GirlsWhoML: Introduction to Machine Learning}, Lecturer and Content Creator
    \item \textbf{Deep learning and Machine learning course}, Course Demonstrator, \textit{CDT Health Data Science, Big Data Institute, University of Oxford}, November 2020
\end{itemize}


\subsection*{Other Activities \& Awards} 
\begin{itemize}
    \item \textbf{Awarded Microsoft Research PhD Fellowship 2021 - 2022}, this includes an internship at Microsoft Research Cambridge that will be undertaken in the summer of 2022.
    \item \textbf{President of Oxford Women in Computer Science (2021 - 2022)}  
    \item \textbf{Attended SeedWISE} - a 7-week program for STEM DPhil students at the university of Oxford to explore career options in industry and enterprise
\end{itemize}